---
title: "Module 3 - Assignment"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: paged
runtime: shiny_prerendered
description: >
  Assignment for Data Management in R module
---


```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(randomNames)

set.seed(1)

Data1 <- data.frame(
  id  = sample(1:100, size = 100),
  village_id = sample(1:8, size = 100, replace = TRUE),
  farmer_name = c(randomNames(50, gender = 0), randomNames(50, gender = 1)),
  gender = c(sample(c("1", "M", "m", "Male"), 50, replace = TRUE), sample(c("2", "F", "f", "Female"), 50, replace = TRUE)),
  farm_area = c(sample(seq(from = 2, to = 25, by = 0.4), 99, replace = TRUE), 100),
  hh_size = sample(c(1:10, -9), size = 100, replace = TRUE),
  income = sample(c(seq(from = 100, to = 900, by = 60), 0, -9), size = 100, replace = TRUE),
  costs = sample(c(seq(from = 50, to = 500, by = 20), -9), size = 100, replace = TRUE)
)

xx <- sample(1:100, 5)

for(i in 1:5){
  Data1$farmer_name[xx[i]] <- paste0(" ", Data1$farmer_name[xx[i]])
}

yy <- 1:100

yy <- yy[-xx]

yy <- sample(1:100, 5)

for(i in 1:5){
  Data1$farmer_name[yy[i]] <- paste0(Data1$farmer_name[yy[i]], " ")
}

```

## Part 1 - Data Cleaing

### Dataset

To start with you will work on the following data set which contains a number of variables about a list of 100 farmers.

```{r, exercise = FALSE}
Data1
```


### Exercise 1a - Trim Whitespace

### Exercise 1b - Missing Data

### Exercise 1c - Correcting labels

### Exercise 1d - Correcting outlier values

### Exercise 1e - Creating a new variable

### Ecercise 1f - Sorting data

## Part 2 - Data Reshaping

### Exercise 2a - Pivot longer

### Exercise 2b - Pivot wider

## Part 3 - Data Merging

### Exercise 3a - Binding

### Exercise 3b - Summarising

### Exercise 3c - Joining data